### 2011-04-23 docs/analysis/analysis.tex
add the analysis chapter to the main document
update and add particle stuff

\section{The {\tt data\_processing} Routines}

@@

@@

>>>>

\section{The {\tt data\_processing} Routines}
\label{sec:analysis}

@@

\item {\tt fvarnames.f90}

  Simply print out the list of variables stored in a plotfile.

@@

\subsection{Particle routines}

The {\tt parseparticles.py} routine in the {\tt python/} subdirectory
can read in MAESTRO particle files containing particle histories
(usually named {\tt timestamp\_??}.  The driver {\tt test.py} shows
shows how to use this module to plot particle histories.
